Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
study [Pérez..." ] fixed

% The Use of Chatbots in Higher Education
The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell
in systems where synchronous conversations take place. 
The use of conversational agents (chatbots) in higher education is
still at its infancy \cite{yang2019opportunities}. Nevertheless,
recent studies examining their positive impact on students' academic
performance \cite{perez2020rediscovering} and engagement
\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
collecting course feedback from students in higher education improved
students' response quality and boosted their enjoyment levels
\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
either tools such as mobile devices or teaching strategies based on
gamification \cite{Yildirim2017} can improve student motivation. In
this sense, the authors in \cite{Pimmer2019} adopted a quasi-experimental, survey-based approach to
report the positive impact of using instant messaging tools in boosting students' knowledge and mitigating their feelings of isolation.

>>>>

% The Use of Chatbots in Higher Education
The use of MIM, although possibly valuable by itself, can be enhanced via the use of chatbots, which, being conversational agents, usually dwell in systems where synchronous conversations take place. 
The use of conversational agents (chatbots) in higher education is
still at its infancy \cite{yang2019opportunities}. Nevertheless,
recent studies examining their positive impact on students' academic
performance \cite{perez2020rediscovering} and engagement
\cite{differ.chat,abbas2021onlinechat} have led to a growing interest
in using this technology in the (possibly virtual) classroom. Indeed, the use of chatbots in
collecting course feedback from students in higher education improved
students' response quality and boosted their enjoyment levels
\cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using
either tools such as mobile devices or teaching strategies based on
gamification \cite{Yildirim2017} can improve student motivation. In
this sense, the authors in \cite{Pimmer2019} carried out a series of experiments with
technological tools whose results showed positive perception and
acceptance of the use of technology in teaching and learning.
